Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-10 code/rmarkdown/article.Rmd
+ added lme4 deps + article eqn fixes
Former-commit-id: b5a36f0ef9e082c351f81972e5c50d983ff49e4f

We investigated the benefits of using surrogate-based targets in prioritizations using generalized linear mixed-effects models fit with logit liknks [GLMMs; using the \texttt{lme4 R} package; @469]. We fit a full model to the proportion of genetic variation secured in a given prioritization. This model contained categorical predictor variables to indicate the combination of targets used to generate the prioritizations (amount-only, amount and surrogate targets, and amount and genetic targets), the scenario that was used to generate the prioritization (single-species, multi-species, and multi-species with cost), the type of genetic variation measured (adaptive and neutral), and all interactions between these variables. We subject the full model to a backwards stepwise term deletion routine to assess term significance. We conducted a post-hoc analysis on the minimal adquate model using Tukey contrasts with a Bonferroni correction [using the \texttt{multcomp R} package; @r470].

@@

<!-- scenario analysis -->
To determine if the addition of environmental and geographic targets could improve the effectiveness of prioritizations in a more realistic context, we generated prioritizations according according to three scenarios using different combinations of targets (Figure 3). We then computed the proportion of adaptive and neutral genetic variation secured in each prioritization (Figure 4). The proportion of genetic variation secured in a prioritization was found to depend on the combination of targets used to generate the prioritization (${\chi^2}_{`r scenario.ANOVA.4.DF$Chi.Df[[2]]`} = `r scenario.ANOVA.4.DF$statistic[[2]]`; $P$ `r pvalString(scenario.ANOVA.4.DF$Pr..Chisq.[[2]])`). Specifically, the amount-based prioritizations tended to secure less variation than the prioritizations generated using additional surrogate ($Z_1 = `r scenario.GLHT.2.DF$statistic[[1]]`$; $P `r pvalString(scenario.GLHT.2.DF$p.value[[1]])`$) or genetic variables ($Z_1 = `r scenario.GLHT.2.DF$statistic[[2]]`$; $P `r pvalString(scenario.GLHT.2.DF$p.value[[2]])`$). No evidence was found to suggest that the prioritizations that included additional surrogate- or genetic-based targets secured a different proportion of genetic variation ($Z_1 = `r scenario.GLHT.2.DF$statistic[[3]]`$; $P `r pvalString(scenario.GLHT.2.DF$p.value[[3]])`$). We also found that the prioritizations tended to secure more adaptive than neutral genetic variation (${\chi^2}_{`r scenario.ANOVA.3.DF$Chi.Df[[2]]`} = `r scenario.ANOVA.3.DF$statistic[[2]]`; $P$ `r pvalString(scenario.ANOVA.3.DF$Pr..Chisq.[[2]])`). We also found significant differences in the average proportion of genetic variation secured by prioritizations in each of the scenarios (${\chi^2}_{`r scenario.ANOVA.2.DF$Chi.Df[[2]]`} = `r scenario.ANOVA.2.DF$statistic[[2]]`; $P$ `r pvalString(scenario.ANOVA.2.DF$Pr..Chisq.[[2]])`). Specifically, both the multi-species ($Z_1 = `r scenario.GLHT.1.DF$statistic[[1]]`$; $P `r pvalString(scenario.GLHT.1.DF$p.value[[1]])`$) and multi-species with cost ($Z_1 = `r scenario.GLHT.1.DF$statistic[[2]]`$; $P `r pvalString(scenario.GLHT.1.DF$p.value[[2]])`$) scenarios were found to secure more genetic variation than the single species scenario. Neither the multi-species scenarios were found to secure a different proportion of genetic variation ($Z_1 = `r scenario.GLHT.1.DF$statistic[[3]]`$; $P `r pvalString(scenario.GLHT.1.DF$p.value[[3]])`$). These results suggest that surrogate-based targets can substantially improve the proportion of genetic variation secured in a prioritization.

>>>>

We investigated the benefits of using surrogate-based targets in prioritizations using generalized linear mixed-effects models fit with logit liknks [GLMMs; using the \texttt{lme4 R} package; @469]. We fit a full model to the proportion of genetic variation secured in a given prioritization. This model contained categorical predictor variables to indicate the combination of targets used to generate the prioritizations (amount-only, amount and surrogate targets, and amount and genetic targets), the scenario that was used to generate the prioritization (single-species, multi-species, and multi-species with cost), the type of genetic variation measured (adaptive and neutral), and all interactions between these variables. This model accomodated prioritizations generated for the same species using a random intercept term. We subject the full model to a backwards stepwise term deletion routine to assess term significance. We conducted a post-hoc analysis on the minimal adquate model using Tukey contrasts with a Bonferroni correction [using the \texttt{multcomp R} package; @r470].

@@

<!-- scenario analysis -->
To determine if the addition of environmental and geographic targets could improve the effectiveness of prioritizations in a more realistic context, we generated prioritizations according according to three scenarios using different combinations of targets (Figure 3). We then computed the proportion of adaptive and neutral genetic variation secured in each prioritization (Figure 4). The proportion of genetic variation secured in a prioritization was found to depend on the combination of targets used to generate the prioritization (${\chi^2}_{`r scenario.ANOVA.4.DF$Chi.Df[[2]]`} = `r scenario.ANOVA.4.DF$statistic[[2]]`$; $P$ `r pvalString(scenario.ANOVA.4.DF$Pr..Chisq.[[2]])`). Specifically, the amount-based prioritizations tended to secure less variation than the prioritizations generated using additional surrogate ($Z_1 = `r scenario.GLHT.2.DF$statistic[[1]]`$; $P `r pvalString(scenario.GLHT.2.DF$p.value[[1]])`$) or genetic variables ($Z_1 = `r scenario.GLHT.2.DF$statistic[[2]]`$; $P `r pvalString(scenario.GLHT.2.DF$p.value[[2]])`$). No evidence was found to suggest that the prioritizations that included additional surrogate- or genetic-based targets secured a different proportion of genetic variation ($Z_1 = `r scenario.GLHT.2.DF$statistic[[3]]`$; $P `r pvalString(scenario.GLHT.2.DF$p.value[[3]])`$). We also found that the prioritizations tended to secure more adaptive than neutral genetic variation (${\chi^2}_{`r scenario.ANOVA.3.DF$Chi.Df[[2]]`} = `r scenario.ANOVA.3.DF$statistic[[2]]`$; $P$ `r pvalString(scenario.ANOVA.3.DF$Pr..Chisq.[[2]])`). We also found significant differences in the average proportion of genetic variation secured by prioritizations in each of the scenarios (${\chi^2}_{`r scenario.ANOVA.2.DF$Chi.Df[[2]]`} = `r scenario.ANOVA.2.DF$statistic[[2]]`$; $P$ `r pvalString(scenario.ANOVA.2.DF$Pr..Chisq.[[2]])`). Specifically, both the multi-species ($Z_1 = `r scenario.GLHT.1.DF$statistic[[1]]`$; $P `r pvalString(scenario.GLHT.1.DF$p.value[[1]])`$) and multi-species with cost ($Z_1 = `r scenario.GLHT.1.DF$statistic[[2]]`$; $P `r pvalString(scenario.GLHT.1.DF$p.value[[2]])`$) scenarios were found to secure more genetic variation than the single species scenario. Neither the multi-species scenarios were found to secure a different proportion of genetic variation ($Z_1 = `r scenario.GLHT.1.DF$statistic[[3]]`$; $P `r pvalString(scenario.GLHT.1.DF$p.value[[3]])`$). These results suggest that surrogate-based targets can substantially improve the proportion of genetic variation secured in a prioritization.
